---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r,echo = TRUE}
library(ggplot2)
Sys.setlocale("LC_TIME", "English")
data<-read.csv(unz("activity.zip", "activity.csv"))
data <- transform(data, date = as.POSIXct(date))
```
## What is mean total number of steps taken per day?
```{r histogram,fig.height= 4}
sumpd<-tapply(data$steps, data$date, sum)
sumpd <- data.frame(date=names(sumpd),steps = sumpd,row.names=NULL)
sumpd  <- transform(sumpd , date = as.POSIXct(date))
par(mar = c(5, 4, 1, 1),las =1)
qplot(date,steps,data = sumpd,geom = "histogram",stat="identity",main = "Histogram of Steps per Day")

mean(sumpd$steps,na.rm= TRUE)
median(sumpd$steps, na.rm = TRUE)
```


## What is the average daily activity pattern?
```{r timeseries,fig.height= 4}
avgin<-tapply(data$steps, data$interval, mean,na.rm = TRUE)
avgin <- data.frame(interval=names(avgin),steps = avgin,row.names=NULL)
par(mar = c(5, 4, 1, 1),las =1)
qplot(interval,steps,data=data,geom = "line",stat="summary",fun.y = "mean",main =" Time Series of Average Number of Steps Taken, Averaged Across All Days")
```

This is the max average number of steps in 5-minute interval.
```{r}
max(avgin$steps)
```


```{r}
mas <- names(which.max(avgin$steps))
```
`r mas` in 5-minute interval contains the maximum number of steps on average across all the days in the dataset.

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
